---
title: "rtweet"
output: 
  html_document:
    keep_md: true
    number_sections: true
    highlight: zenburn
    toc: yes
editor_options: 
  chunk_output_type: inline
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "figs/tweet-"
)
```

* http://rtweet.info/


```{r import libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(rtweet)
library(stringr)
library(tidyverse)
library(tidytext)
options(stringsAsFactors = F)
```

# token

* Using `sessionInfo()` to check if your rtweet version is later than 0.6.7. If not, using `install.packages()` to re-install the package.

* ...(copy from the page)...The `create_token()` function should automatically save your token as an environment variable for you. To make sure it worked, compare the created token object to the object returned by `get_token()`


* Visiting rtweet package doc to see how to authenticate
```
twitter_token <- create_token(
  app = appname,
  consumer_key = key,
  consumer_secret = secret,
  access_token = access_token,
  access_secret = access_secret
)

## check to see if the token is loaded
identical(twitter_token, get_token())
```

```{r}
token1 <- create_token(app = "TaiwanProtessAnalysis",
                       consumer_key = "2KkDfxFu3j4giYxir4FQI1lgW",
                       consumer_secret = "yfDBjY00fBbn7VN0IQHodYNQE7SvJrsJIoLJfNzviLPGdICPK0",
                       access_token = "53118769-81DvfPmWkT33TZfcQsyOJ6XE4vGzGj1ssIOsZyuTg",
                       access_secret = "pB6me2dmWQOHTouPDf0JXYmdIzXeZmCLeFtDatx0lxewf")
```




# search_tweets()
* arguments: `max_id = ` and `since_id = `



```{r}
topics <- c("#metoo", "prom dress", "taiwan", "#climatechange", "#nuclear", "#china")
q <- "#china"
rt <- search_tweets( q, n = 1000,
  retryonratelimit = TRUE, include_rts = T
)
saveRDS(rt, file = 
          sprintf("data/%s.rt.%s.rds", gsub(" ", "_", q),
                  as.character(strftime(Sys.time(), "%y%m%d%H%M"))))
min.id <- min(rt$status_id)
max.id <- max(rt$status_id)
```
##　timestamp summary
```{r}
rt$created_at %>% summary
```




# combining data
```{r}
rt$created_at %>% summary

ts_plot(rt, "5 mins") +
  ggplot2::theme_minimal() +
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of tweets related to prom dress event",
    subtitle = "Twitter status (tweet) counts aggregated using hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
```



# Get timeline
```{r}
user_id <- "daumkeziah"
rt.u <- get_timeline(user_id, n = 3200)
```

