---
title: "Paid Maternity Leave"
author: "Jilung Hsieh"
date: "2018/7/2"
output: 
  html_document: 
    number_sections: true
    highlight: textmate
    theme: spacelab
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 案例：產假支薪

* 本案例將利用R來重製華盛頓郵報在2016/08/13的一篇談論美國婦女產假支薪情形的報導。這個案例中將會應用到data.frame和基本的繪圖與資料摘要方法。The case adaped Washington Post's paid maternity leave as an exmaple to introduce basic skill of data.frame, plotting, and data mamipulation.

* 原始新聞來源：https://www.washingtonpost.com/news/worldviews/wp/2016/08/13/the-world-is-getting-better-at-paid-maternity-leave-the-u-s-is-not/?tid=sm_tw&utm_term=.f8cd50280326#comments


# 用readxl套件讀Excel檔

* readxl也包含在tidyverse的套件集中，所以應該已經在前次安裝過，不用特別安裝。
 
```{r}
library(readxl)
options(stringsAsFactors = FALSE)
```

# 乾淨的完整版程式
```{r}
ldata <- read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T)

# select columns by index
matleave <- ldata[ , c(3, 6:24)]
str(matleave)

# select all NA cells and assign 0 to them
matleave[is.na(matleave)] <- 0

# filter rows by condition
m5 <- matleave[matleave$'matleave_13' == 5, ]

# filter rows by condition
m55<- m5[m5$'matleave_95' == 5,]

# plot
par(mfrow=c(4,6), mai= c(0.2, 0.2, 0.2, 0.2))
for (i in c(1:nrow(m55))){
	barplot(unlist(m55[i,-1]),
			border=NA, space=0,xaxt="n", yaxt="n", ylim = c(0,5))
	title(m55[i,1], line = -4, cex.main=3)
}
```





# 學習者版本
* 利用`?read_excel`查詢一下可以怎麼用。read_excel() convert a sheet to a data.frame
```
read_excel(path, sheet = NULL, range = NULL, col_names = TRUE,
		   col_types = NULL, na = "", trim_ws = TRUE, skip = 0, n_max = Inf,
		   guess_max = min(1000, n_max))

```

## 載入並觀察
```{r}
ldata <- read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T)

# View(ldata)
class(ldata)		# [1] "tbl_df"     "tbl"        "data.frame"
dim(ldata)

# Show names of variables (vectors, columns) by names()
names(ldata)
```




## 選擇所需的變項

```{r}
matleave <- ldata[ , c(3, 6:24)]
class(matleave)
dim(matleave)
str(matleave)
```



## 取代NA

* `NA: Not Available`
* `v[is.na(v)]` will select all NA cells
* 以0取代NA的資料格。避免繪圖產生錯誤
* `sum(is.na(matleave))`的目的是檢測還有沒有NA值。如果有的話`is.na()`就會是`TRUE`，那麼加總後，如果不是0，那就代表還有NA。

```{r}
matleave[is.na(matleave)] <- 0

# checks if there are still NA cells.
anyNA(matleave)

sum(is.na(matleave))
```




## 繪圖

* Plotting the second rows and all columns except 1st column
* **Question** 為何要`unlist()`？請試著執行`barplot(matleave[2, -1])`這個沒有`unlist()`的版本，看看會有什麼錯誤訊息。資料結構有何差異呢？
* 嘗試用`class()`或`str()`嘗試觀察沒有`unlist()`版本的資料，看看資料型態和有`unlist()`的會有何不同？

```{r}
barplot(unlist(matleave[2, -1]))

# Take a look at the data type of matleave[2, ]
class(matleave[2, -1])

# Using unlist() to convert a single row dataframe to a vector
unlist(matleave[2, -1])
class(unlist(matleave[2, -1]))

# Add more arguments
barplot(unlist(matleave[2, -1]))
barplot(unlist(matleave[2, -1]), ylim=c(0, 5))
barplot(unlist(matleave[2, -1]), ylim=c(0, 5), space=0)
barplot(unlist(matleave[2, -1]), ylim=c(0, 5), space=0, border=NA)
barplot(unlist(matleave[2, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
```




### 在data.frame中選擇資料

```{r}
# View(matleave[1]) # select the 1st variable
# View(matleave[ ,1]) # select the 1st column
# View(matleave[1, ]) # select the 1st row

class(matleave[1])		# "tbl_df"     "tbl"        "data.frame"
class(matleave[ ,1])	# "tbl_df"     "tbl"        "data.frame"
class(matleave[1, ])	# "tbl_df"     "tbl"        "data.frame"
class(matleave$iso3)	# character (vector)

```




## for-loop

* 底下可以看見每一行非常相似且一致的特徵，僅有`matleave`內的索引由1被列出至6。因此，最好的方法是用迴圈（for-loop）的方式將相同的程式碼，從1~6之間做六次。

```{r}
barplot(unlist(matleave[1, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
barplot(unlist(matleave[2, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
barplot(unlist(matleave[3, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
barplot(unlist(matleave[4, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
barplot(unlist(matleave[5, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
barplot(unlist(matleave[6, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")

```

* 使用for-loop的版本

```{r}
for(i in 1:6){
  barplot(unlist(matleave[i, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
}

```


# 繪製子圖

* Check `?par` to get paremeters of plotting

* `**mai**`: A numerical vector of the form c(bottom, left, top, right) which gives the margin size specified in inches.

* `**mfcol, mfrow**`:A vector of the form c(nr, nc). Subsequent figures will be drawn in an nr-by-nc array on the device by columns (mfcol), or rows (mfrow), respectively.


```{r}
par(mfrow=c(3,2), mai= c(0.2, 0.2, 0.2, 0.2))
for(i in 1:6){
  barplot(unlist(matleave[i, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
}

```


## Practice

```{r}
# plot more rows to see what happens
par(mfrow=c(3,2), mai= c(0.2, 0.2, 0.2, 0.2))
for(i in 1:10){
    barplot(unlist(matleave[i, -1]), ylim=c(0, 5), space=0, border=NA, xaxt="n", yaxt="n")
}

# plot all subplots in a figure

```






# Filter data by the last year value

```{r}
m5 <- matleave[matleave$'matleave_13'==5, ]
nrow(m5)

# matleave$'matleave_13'
# matleave$'matleave_13'==5
# length(matleave$'matleave_13'==5)
```




# Filter data by the first year value

```{r}
# filter rows whose 'matleave_95' is 5
m55<- m5[m5$'matleave_95'==5,]

# filter rows whose 'matleave_95' is not 5
m05<- m5[m5$'matleave_95'!=5,]

```



# Plot m55
```{r}
nrow(m55)

par(mfrow=c(4, 6), mai= c(0.2, 0.2, 0.2, 0.2))
for (i in 1:nrow(m55)){
  barplot(unlist(m55[i, -1]), border=NA, space=0, xaxt="n", yaxt="n", ylim = c(0,5))
}


# How do you add title for each subplot?
par(mfrow=c(4,6), mai= c(0.2, 0.2, 0.2, 0.2))
for (i in 1:nrow(m55)){
    barplot(unlist(m55[i, -1]), border=NA, space=0,xaxt="n", yaxt="n", ylim = c(0,5))
	title(m55[i,1], line = -4, cex.main=3)
}

```




# Practice
```{r}
# plotting matleave_95 != 5 but matleve_13 == 5

# plotting for matleave_13 == 4

# Select, and filter data in dplyr form

```


# by dplyr
```{r}
library(dplyr)
m55 <- ldata %>%
    select(iso3, contains("matleave"), -contains("wrr")) %>%
    mutate_if(is.numeric, function(x){ifelse(is.na(x), 0, x)}) %>%
    filter(matleave_13==5, matleave_95==5)

```



## More: gather() to long-form

```{r}
library(tidyr)
# Gather 2:20 column to a new variable "year"
# Name level data as "degree"
long_form <- gather(matleave, "year", "degree", 2:20)

```




# Drawing worldmap

```{r}
# install.packages("rworldmap")
library(rworldmap)# drawing worldmap

# select cols
mdata <- ldata[,c(3, 6:24)]

# join your data with the world map data
myMap <- joinCountryData2Map(mdata, joinCode = "ISO3", nameJoinColumn = "iso3")
# 196 codes from your data successfully matched countries in the map
# 1 codes from your data failed to match with a country code in the map
# 47 codes from the map weren't represented in your data

myMap$matleave_13


# Draw world maps
dev.off()
mapCountryData(myMap
               , nameColumnToPlot="matleave_13"
               , catMethod = "categorical"
)


# self-defined colors
colors <- c("#FF8000", "#A9D0F5", "#58ACFA", "#0080FF", "#084B8A")
mapCountryData(myMap
			   , nameColumnToPlot="matleave_13"
			   , catMethod = "categorical"
			   , colourPalette = colors
			   , addLegend="FALSE"
)

```




# Practice

* Drawing map for the first year
* Remember to setting `par()` for plotting as subplots

```{r}
par(mfrow=c(4,5), mai= c(0.2, 0.2, 0.2, 0.2))
for(i in 51:69){
    mapCountryData(myMap
                   , nameColumnToPlot=names(myMap)[i]
                   , catMethod = "categorical"
                   , colourPalette = colors
                   , addLegend="FALSE"
                   )
}
```




# Summarize data

```{r}
# select 1 to 24 vectors
tdata <- ldata[ ,1:24]
names(tdata)

# deal with NAs
tdata[is.na(tdata)] <- 0

# create contigency table by region for matleave_13: data count by length()
num <- tapply(ldata$matleave_13, ldata$region, length)

# tapply() using mean(), sum(), and sd
total <- tapply(ldata$matleave_13, ldata$region, mean)
average <- tapply(ldata$matleave_13, ldata$region, sum)
sd <- tapply(ldata$matleave_13, ldata$region, sd)

# create data frame for about variables
res <- data.frame(num, average, total, sd)
# View(res)

```



# Grouping data: merge rows by category

```{r}
byregion <- aggregate(tdata[,6:24], by=list(tdata$region), mean)
# View(byregion)
byregion.sd <- aggregate(tdata[,6:24], by=list(tdata$region), sd)
?aggregate

head(byregion)

```




# Plotting results

```{r}
# Line ploting the 1st row
dev.off()
plot(unlist(byregion[1,]), type="o")

# Line ploting the 2nd~6th rows
plot(unlist(byregion[2,]), type="o")
plot(unlist(byregion[3,]), type="o")
plot(unlist(byregion[4,]), type="o")
plot(unlist(byregion[5,]), type="o")
plot(unlist(byregion[6,]), type="o")



# Using for-loop and par() to plot all graph
par(mfrow=c(3,2), mai= rep(0.3, 4))
for (i in 1:6){
    plot(unlist(byregion[i,-1]), type="o", ylim=c(0, 5))
	title(byregion[i,1])
}

```



## The fittest version to compute staySame
```{r}
# staySame version
# staySame <- apply(m5[,2:20], 1, function(x) length(unique(x[!is.na(x)]))) 
# m55 <- m5[staySame, ]
# m50 <- m5[!staySame, ]

```





# by dplyr

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)

long_form <- gather(matleave, "year", "degree", 2:20)

matleave <- ldata %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95==5) %>%
	gather("year", "degree", 2:20) %>%
	replace_na(list(degree=0)) %>%
	mutate(year2=as.POSIXct(strptime(year, "matleave_%y"))) %>%
	mutate(year3 = strftime(year2, "%Y"))

matleave %>%
	ggplot() +
	aes(year3, degree) +
	facet_grid(iso3~.) +
	geom_bar(stat = "identity", fill = "blue")

```




