---
title: "9_2_cosine_similarity"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(tidyverse)
library(stringr)
library(tidytext)
library(jiebaR)
options(stringsAsFactors = FALSE)

```


# cosine similarity
```{r}
eng <- "The dog run A cat run A dog sleep The cat sleep A dog bark The cat meows The bird fly A bird sleep"

mutual_grams <- data.frame(w1 = unlist(str_split(eng, "\\s"))) %>% 
	mutate(w2 = lead(w1, 1)) %>%
	filter(complete.cases(.)) %>%
	bind_rows(data.frame(w1 = .$w2, w2 = .$w1))

affmatrix <- mutual_grams %>%
	count(w1, w2) %>%
	spread(w2, n, fill = 0) %>%
	`rownames<-`(.$w1) %>%
	select(-w1)
```


```{r}
affmatrix["dog",]
affmatrix[,"dog"]
affmatrix[c("dog" ,"cat"),]
affmatrix[c("dog" ,"bird"),]
```

## calculating cosine similarity
* possible solution. https://www.rdocumentation.org/packages/tcR/versions/2.2.1.11
* Build a Simple Cosine Similarity Search Engine in R http://rstudio-pubs-static.s3.amazonaws.com/266142_e947ad96bead4abdb3d0fa8a539f7511.html
* The cosine measure is nearly identical with the pearson correlation coefficient (besides a constant factor) cor(method="pearson"). For an investigation on the differences in the context of textmining see (Leydesdorff, 2005).
	* https://www.rdocumentation.org/packages/lsa/versions/0.73.1/topics/cosine
	* References: Leydesdorff, L. (2005) Similarity Measures, Author Cocitation Analysis,and Information Theory. In: JASIST 56(7), pp.769-772.

## (to test) method 1?
* https://stats.stackexchange.com/questions/31565/is-there-an-r-function-that-will-compute-the-cosine-dissimilarity-matrix
```
# input: row matrices 'ma' and 'mb' (with compatible dimensions)
# output: cosine similarity matrix

cos.sim=function(ma, mb){
  mat=tcrossprod(ma, mb)
  t1=sqrt(apply(ma, 1, crossprod))
  t2=sqrt(apply(mb, 1, crossprod))
  mat / outer(t1,t2)
}
```


## method 2 byself
```{r}
sum(affmatrix['cat',]*affmatrix['dog',])/(sqrt(sum(affmatrix['cat']^2))*sqrt(sum(affmatrix['dog']^2)))

sum(affmatrix['bird',]*affmatrix['dog',])/(sqrt(sum(affmatrix['bird']^2))*sqrt(sum(affmatrix['dog']^2)))
```

# SVD to reduce dimension to plot

```{r}
m.svd <- svd(affmatrix)
D <- diag(m.svd$d)
m.svd$u %*% D %*% t(m.svd$v)    # X = U D V'

plot(m.svd$u)
text(m.svd$u[,1], m.svd$u[,2], labels=rownames(affmatrix), cex= 0.7)
plot(m.svd$d)
```

## plot SVD results
* 因為是一個m*m矩陣，所以看u或v幾乎沒差。
```{r}
plot(m.svd$v)
text(m.svd$v[,1], m.svd$v[,2], labels=rownames(affmatrix), cex= 0.7)
View(m.svd$u)
View(m.svd$v)
m.svd$d
library(lattice)
levelplot(m.svd$u)
levelplot(m.svd$v)
```

# Load trump's tweets
```{r}
raw.df <- readRDS("data/alltweets.rds")

# raw.df %>% summary()
filtered.df <- raw.df %>%
    filter(!str_detect(text, '^"')) %>%
    filter(str_detect(text, "nytime|fox|news"))
    # filter(timestamp > as.POSIXct("2017-01-01") & 
    #            timestamp < as.POSIXct("2017-05-08")) 

data(stop_words)
unnested.df <- filtered.df %>%
    mutate(text = str_replace_all(text, 
                                  "https://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
    # unnest_tokens(word, text, drop = FALSE) %>%
    unnest_tokens(word, text, 
                  token = "regex", pattern = "[^A-Za-z\\d#@']", 
                  drop=FALSE) 
# %>%
#     anti_join(stop_words)
```


## build affmatrix for trump's data
```{r}
mutual_grams.trump <- unnested.df %>%
    select(id_str, w1 = word) %>%
    group_by(id_str) %>%
    mutate(w2 = lead(w1, 1)) %>%
    ungroup() %>%
    filter(complete.cases(.)) %>% 
    bind_rows(data.frame(id_str = .$id_str, w1 = .$w2, w2 = .$w1))
    
affmatrix.trump <- mutual_grams.trump %>%
	count(w1, w2) %>%
	spread(w2, n, fill = 0) %>%
	`rownames<-`(.$w1) %>%
	select(-w1)
```



## (STOP) SVD
* "Never end, never end, ...."
```
# svd.trump <- svd(affmatrix.trump)
```

## (TRY) tsne
* time-consumed but workable
```{r}
library(tsne)
res <- tsne(affmatrix.trump, initial_config = NULL, k = 2, initial_dims = 30, perplexity = 30, max_iter = 500, min_cost = 0, epoch_callback = NULL, whiten = TRUE,
epoch=100)
```
## plotting
```{r}
as.data.frame(res) %>%
    bind_cols(data.frame(name = rownames(affmatrix.trump))) %>%
    filter(V1 > 0, V2 > 0) %>%
    ggplot(aes(V1, V2, label = name)) +
    geom_jitter(alpha = 0.1, color = "blue") + 
    geom_text(aes(label = name),
              hjust=0, vjust=0, size = 4, alpha = 0.5)
```


## (TRY) t-sne by Rtsne
* https://www.r-bloggers.com/playing-with-dimensions-from-clustering-pca-t-sne-to-carl-sagan/
* t-sne is often compared to PCA, SVD or other dimensional reduction method.
* Rtsne: https://rpubs.com/marwahsi/tnse







## (Deprecated) Alan's cosine similarity
```
eng <- unlist(strsplit(eng," "))

options(stringsAsFactors = F)
word2DR <- function(data_1){
	test1 <- unlist(data_1)
	alls <- sapply(1:length(test1),function(x){
		paste(c(test1[x],test1[x+1]),collapse = " ")
	})
	alls <- alls[-length(alls)]
	alls <- data.frame(alls=alls)
	alls <- alls%>%separate(alls,c("first","second"),sep=" ")
	test <- data.frame(tapply(alls$first,list(alls$first, alls$second),length))
	test2 <- data.frame(t(test))
	if(ncol(test)>ncol(test2)){
		name <-colnames(test)[which(!colnames(test)%in%colnames(test2))]
		num <- which(!colnames(test)%in%colnames(test2))
		x1 <- c(rep(0,nrow(test2)))
		test <- rbind(test[1:num-1,],x1,test[num:nrow(test),])
		test2 <- cbind(test2[,1:num-1],x1,test[,num:ncol(test2)])
		rownames(test)[num] <- name
		colnames(test2)[num]<- name
	}
	else if(ncol(test2)>ncol(test)){
		name <-colnames(test2)[which(!colnames(test2)%in%colnames(test))]
		num <- which(!colnames(test2)%in%colnames(test))
		x1 <- c(rep(0,nrow(test)))
		test <- cbind(test[,1:num-1],x1,test[,num:ncol(test)])
		test2 <- rbind(test2[1:num-1,],x1,test2[num:nrow(test2),])
		rownames(test)[num] <- name
		colnames(test2)[num]<- name
		
	}
	
	test[is.na(test)] <- 0
	test2[is.na(test2)] <- 0
	final <- test+test2
	return(final)
}


ha <- word2DR(eng)

sum(ha['cat',]*ha['dog',])/c(sqrt(sum(ha['cat']^2))*sqrt(sum(ha['dog']^2)))
sum(ha['bird',]*ha['dog',])/c(sqrt(sum(ha['bird']^2))*sqrt(sum(ha['dog']^2)))

```

